%!TEX root = ../docs-requirements.tex
%% *************************************************************************
%% TerraMICRO
%% Mission and System Requirements Specification
%%
%% This document shall list and describe all mission requirements, their 
%% criteria for success, and (when applicable) methods by which these 
%% requiremnts shall be evaluated.
%%
%% The intent of this specification is to quantify and control the criteria
%% by which mission success is defined, and to provide traceability to each
%% subsystem's performance to ensure mission success is achieved by the 
%% vehicle's design.
%%
%% Created November 26, 2018 by Phil Linden
%% *************************************************************************

\subsection{Engineering \& Technology Objectives}
\subsubsection{Balloon Monitoring}
A system will be able to monitor the temperature and pressure within a balloon
and report that back to the HAB payload.


\subsubsection{Payload design (\textmu HAB)}
Flight test microHAB-- a flexible, expandable, and cost-effective platform to
support many different mission profiles/payloads and includes all of the basics
for a HAB launch. 
% \cite{dans microhab design doc}

\subsubsection{Altitude regulation}
Limit maximum altitude and rate of ascent by thecontrolled release of helium
during flight to prolong the mission duration. Maintain 75,000 feet altitude
for at least 30 minutes. 

\subsubsection{High quality video}
Horizon-looking full color video at 1080p\@30 fps or better (1080p\@60fps or
4K\@30fps preferred).

\subsubsection{Video capture burst event}
Capture the balloon burst event with minimum resolution of 720p\@60fps or 
better. (720p\@120fps or 1080p\@120fps preferred)

\subsection{Science Objectives}
\subsubsection{NDVI vegetation density}
Use NDVI with a commercially available RGB (VNIR) camera to estimate vegetation
density from images in real time during flight. Minimum video quality
480p\@30fps.

\subsection{Key Design Features}
There are several design features that are specific requests from TerraHAB
engineers. The flight system should meet these requests or provide justification
for not including them.

\begin{itemize}
    \item Externally accessible remove before flight pin(s). 
    \item Include displays and self-test and status check codes to ensure that the balloon is stable and behaving nominally for flight.
    \item Power pin (included in microhab), startup sequence pin, launch pin, etc.
    \item Simplify filling during launch preparations and provide a quick-disconnect from helium filling.
\end{itemize}
 
\subsection{Key Design Requirements}
There are some additional features that are essential for a successful small HAB
flight system.

\begin{itemize}
    \item Multiple independent cut-down mechanisms
    \item Redundant tracking systems
    \item 3 to 6 hours of powered flight time
    \item Under 6 lbs.
\end{itemize}
